
# Descriptive Analysis

## Load packages


### Load basic package

```{r}
library(sp)
library(sf)
library(rgeos)
library(tmap)
library(tmaptools)
library(maptools)
library(tidyverse)
library(spdep)
library(janitor)
library(rgdal)
```

### Load plot library

```{r}
library(ggplot2)
library(RColorBrewer)
```




## Load data


### Load charge point registry.csv file


```{r}
charge <- read_csv("datasets/national-charge-point-registry.csv")
summary(charge$chargeDeviceStatus)
```


### Load London wards shapefile

```{r}
londonwards <- st_read("datasets/wards/London_Ward_CityMerged.shp") %>% 
  st_transform(., 27700)
```




## Filter data



```{r}
chargepoints <- charge [charge$chargeDeviceStatus=="In service" & !is.na(charge$latitude) & !is.na(charge$longitude),] 
```


### Function to filter year (2014, 2017, 2020 register)

```{r}
filterfun <- function(end){
  enddate <- end
  
  filterpoints <- chargepoints %>% 
    filter(chargepoints$dateCreated<=enddate)
  return(filterpoints)
}

```


### Function to transform projection & crop to London

```{r}
londonPfun <- function(end){
  filteredpoints <- filterfun(end)
  transpoints <- filteredpoints %>% 
    select(., c(3,4,5)) %>% 
    st_as_sf(., coords = c("longitude", "latitude"),crs = 4326) %>% 
    st_transform(., 27700) %>%
    distinct()
  
  charge_london <- st_intersects(londonwards, transpoints)
  londonpoints <- transpoints[unlist(charge_london),]
  return(londonpoints)
}
```


### Instance object


```{r}
trend <- data.frame(date=c("2012", "2013", "2014", "2015", "2016",
                           "2017", "2018", "2019", "2020"),
                    count=c(nrow(londonPfun("2012-12-31")),nrow(londonPfun("2013-12-31")),
                            nrow(londonPfun("2014-12-31")),nrow(londonPfun("2015-12-31")),
                            nrow(londonPfun("2016-12-31")),nrow(londonPfun("2017-12-31")),
                            nrow(londonPfun("2018-12-31")),nrow(londonPfun("2019-12-31")),
                            nrow(londonPfun("2020-12-31"))))
```

```{r}
ggplot(data = trend, mapping = aes(x = date, y = count, group = 1)) +
  geom_line(alpha = 0.7)+
  geom_point(alpha = 0.6)+
  geom_text(aes(label = count), vjust = "inward", hjust = "outward", size=3.5)+
  xlab("Year")+
  ylab("Number of charging points")+
  ggtitle("Trend of charging infrastructure deployment in London")+
  theme(axis.title = element_text(size=18),axis.text = element_text(size=16),
        strip.text = element_text(size=18))+
  labs(color = "Development trend")+
  theme_classic() 
```
```{r}
ggsave("pic/charge points trend.jpg", width = 7, height = 4)
```

```{r}
londonpoints2018 <- londonPfun("2018-12-31")
londonpoints2019 <- londonPfun("2019-12-31")
londonpoints2020 <- londonPfun("2020-12-31")
```

### Function to map charge point density by wards


```{r}
pointsjoinedfun <- function(londonpointsyear){
  londonpointsyear <- londonpointsyear
  charge_points_ward <- londonpointsyear[londonwards,]
  
  points_wards <- londonwards%>%
    st_join(charge_points_ward)%>%
    add_count(NAME)%>%
    janitor::clean_names()%>%
    #then density of the points per ward
    mutate(density=(n/hectares)*1000) %>% 
    mutate(id=1) %>% 
    mutate(sumpoints=aggregate(n~id,.,FUN=sum)) %>% 
    mutate(percentage=((n/sumpoints[1, 2]))*100) %>% 
    #select density and other variables 
    dplyr::select(density, percentage, name, gss_code, n) %>% 
    distinct(., gss_code, .keep_all = TRUE)
  
  points_wards <- points_wards %>%                    
    group_by(gss_code) %>%         
    summarise(density=density,
              percentage=percentage,
              wardname=name,
              chargepointcount=n)
  return(points_wards)
}
```

### Save charge points by wards

```{r}
points_wards <- pointsjoinedfun(londonpoints2020) %>% 
  st_drop_geometry()
write.table(points_wards,"created datasets/points_wards.csv",row.names=FALSE,col.names=TRUE,sep=",")
```


```{r}
densityfun <- function(londonpointsyear, number, mode){
  points_wards <- pointsjoinedfun(londonpointsyear)
  tmap_mode(mode)
  breaks = c(0, 20, 30, 40, 50, 60, 200, 400, +Inf) 
  tm <- tm_shape(points_wards) +
    tm_polygons("density",
                breaks=breaks,
                palette=RColorBrewer::brewer.pal(8, "YlOrRd"),
                midpoint=NA) +
    tm_legend(show=FALSE)+
    tm_layout(frame=FALSE)+
    tm_credits(number, position=c(0,0.85), size=1)
  
  return(tm)
}

```
```{r}
legendfun <- function(londonpointsyear){
  points_wards <- pointsjoinedfun(londonpointsyear)
  
  breaks = c(0, 20, 30, 40, 50, 60, 200, 400, +Inf) 
  legend <- tm_shape(points_wards) +
    tm_polygons("density",
                breaks=breaks,
                palette=RColorBrewer::brewer.pal(8, "YlOrRd"), 
                title="Density of Charge Points in London \n(per thousand hectare)") +
    tm_scale_bar(position=c(0.4, 0.01), text.size=0.6)+
    tm_compass(north=0, position=c(0.75, 0.3))+
   
    tm_layout(title = "Charge Points Density Trend", 
              legend.title.size=1,
              legend.text.size = 0.6,
              legend.only = TRUE, 
              legend.position=c(0.1,0.1),asp=0.1)
  
  return(legend)
}
```


### Tmap - charge point density by ward

```{r}

tm1 <- densityfun(londonpoints2018, "a)", "plot")
tm2 <- densityfun(londonpoints2019, "b)", "plot")
tm3 <- densityfun(londonpoints2020, "c)", "plot")
```


```{r}
legend <- legendfun(londonpoints2020)


t_density <- tmap_arrange(tm1, tm2, tm3, legend, ncol=2)
t_density
```
```{r}
tmap_save(t_density, 'pic/london charge points density.png', width=7, height=4)
```

```{r}

tm1v <- densityfun(londonpoints2018, "a)", "view")
tm2v <- densityfun(londonpoints2019, "b)", "view")
tm3v <- densityfun(londonpoints2020, "c)", "view")
```


```{r}
legend <- legendfun(londonpoints2020)


t_densityv <- tmap_arrange(tm1v, tm2v, tm3v, ncol=1)
t_densityv
```

