# Spatial Autocorrelation Analysis

Considering the spatial lags of variables, variables in neighboring geographical units could be calculated, following the first order queen contiguity strategy, which classifies neighbors of geographical units by the sharing of either point or line segment borders. Followed by that, Global Moran’s I and Local Moran’s I statistics for charge points in London could be conducted. 


## Run Global Moran's I

### Function to calculate the centroids

```{r}
# library(spdep)
# First calculate the centroids of all Wards in London

coordsWfun <- function(londonpointsyear){
  points_wards <- pointsjoinedfun(londonpointsyear)
  coordsW <- points_wards %>% 
    st_centroid() %>%
    st_geometry()
}

```
```{r}
# test
coordsW <- coordsWfun(londonpoints2020)
plot(coordsW,axes=TRUE)
```


### Function to create a neighbours list

```{r}
#create a neighbours list
ward_nbfun <- function(londonpointsyear){
  points_wards <- pointsjoinedfun(londonpointsyear)
  ward_nb <- points_wards %>% 
    poly2nb(., queen=T)
  return(ward_nb)
}

```
```{r}
# test
ward_nb20 <- ward_nbfun(londonpoints2020)
plot(ward_nb20, st_geometry(coordsW), col="red")
# add a map underneath
points_wards <- pointsjoinedfun(londonpoints2020) 
plot(points_wards$geometry, add=T)
```

### Function to create spatial weights

```{r}
#create a spatial weights object from these weights
ward_lwfun <- function(londonpointsyear){
  ward_lw <- ward_nbfun(londonpointsyear) %>% 
    nb2listw(., style="C")
  return(ward_lw)
}
```
```{r}
# test
ward_lw20 <- ward_lwfun(londonpoints2020)
head(ward_lw20$neighbours)
```


### Function to run Global Moran's I

```{r}
I_ward_globalfun <- function(londonpointsyear){
  ward_lw <- ward_lwfun(londonpointsyear)
  
  I_ward_global <- londonpointsyear %>% 
    pointsjoinedfun(.) %>% 
    pull(density) %>%
    as.vector()%>% # Converts a distributed matrix into a non-distributed vector
    moran.test(., ward_lw) # density <-> spatial (similar or not)
  return(I_ward_global)
}

```


### Global Moran's I for 2018, 2019, 2020

```{r}
I_ward_global18 <- I_ward_globalfun(londonpoints2018)
I_ward_global19 <- I_ward_globalfun(londonpoints2019)
I_ward_global20 <- I_ward_globalfun(londonpoints2020)

```
```{r}
I_ward_global18
I_ward_global19
I_ward_global20

```


## Run Local Moran's I

### Function to run Local Moran's I

```{r}
ward_lw20 <- ward_lwfun(londonpoints2020)
  
  I_ward_local_count <- londonpoints2020 %>% 
    pointsjoinedfun(.) %>% 
    pull(chargepointcount) %>%
    as.vector()%>% 
    localmoran(., ward_lw20) %>% 
    as_tibble()
  I_ward_local_density <- londonpoints2020 %>% 
    pointsjoinedfun(.) %>% 
    pull(density) %>%
    as.vector()%>% 
    localmoran(., ward_lw20) %>% 
    as_tibble()

slice_head(I_ward_local_count, n=5)
slice_head(I_ward_local_density, n=5)
```


```{r}
# use the local moran function to generate I for each ward in the city

I_ward_localfun <- function(londonpointsyear){
  ward_lw <- ward_lwfun(londonpointsyear)
  
  I_ward_local_count <- londonpointsyear %>% 
    pointsjoinedfun(.) %>% 
    pull(chargepointcount) %>%
    as.vector()%>% 
    localmoran(., ward_lw) %>% 
    as_tibble()
  I_ward_local_density <- londonpointsyear %>% 
    pointsjoinedfun(.) %>% 
    pull(density) %>%
    as.vector()%>% 
    localmoran(., ward_lw) %>% 
    as_tibble()
  
  tm_local_moran <- londonpointsyear %>% 
    pointsjoinedfun(.) %>%
    mutate(charge_count_I = as.numeric(I_ward_local_count$Ii))%>%
    mutate(charge_count_Iz =as.numeric(I_ward_local_count$Z.Ii))%>%
    mutate(density_I =as.numeric(I_ward_local_density$Ii))%>%
    mutate(density_Iz =as.numeric(I_ward_local_density$Z.Ii))
  
  return(tm_local_moran)
}

```


### Function to run tmap for Local Moran's I

```{r}
tmap_local_moranfun <- function(londonpointsyear, number, mode){
  breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
  MoranColours<- rev(brewer.pal(8, "RdBu"))
  tm_local_moran <- I_ward_localfun(londonpointsyear)
  tmap_mode(mode)
  tmap <- tm_shape(tm_local_moran) +
    tm_polygons("charge_count_Iz",
        style="fixed",
        breaks=breaks1,
        palette=MoranColours,
        midpoint=NA)+
    tm_legend(show=FALSE)+
    tm_layout(frame=FALSE)+
    tm_credits(number, position=c(0,0.85), size=1)
  return(tmap)
}
```
```{r}
tmap_moranlegendfun <- function(londonpointsyear){
  breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
  MoranColours<- rev(brewer.pal(8, "RdBu"))
  tm_local_moran <- I_ward_localfun(londonpointsyear)
  legend <- tm_shape(tm_local_moran) +
    tm_polygons("charge_count_Iz",
                breaks=breaks1,
                palette=MoranColours,
                title="Local Moran's I, Charge Points in London") +
    tm_scale_bar(position=c(0.1,0.04), text.size=0.6)+
    tm_compass(north=0, position=c(0.65,0.2))+
   
    tm_layout(title = "Charge Points Local Moran's I", 
              legend.title.size=1,
              legend.text.size = 0.6,
              legend.only = TRUE, 
              legend.position=c(0.1,0.25),asp=0.1)
  
  return(legend)
}
```


```{r}
tm_local_moran18 <- tmap_local_moranfun(londonpoints2018, "a)", "plot")
tm_local_moran19 <- tmap_local_moranfun(londonpoints2019, "b)", "plot")
tm_local_moran20 <- tmap_local_moranfun(londonpoints2020, "c)", "plot")
```
```{r}
moran_legend <- tmap_moranlegendfun(londonpoints2020)

local_moran <- tmap_arrange(tm_local_moran18, 
                            tm_local_moran19, 
                            tm_local_moran20, 
                            moran_legend, ncol=2)
local_moran
```

```{r}
tmap_save(local_moran, "pic/Local Moran's I, Charge Points in London.png",width=7, height=4)
```
```{r}
tm_local_moran18v <- tmap_local_moranfun(londonpoints2018, "a)", "view")
tm_local_moran19v <- tmap_local_moranfun(londonpoints2019, "b)", "view")
tm_local_moran20v <- tmap_local_moranfun(londonpoints2020, "c)", "view")
```
```{r}
moran_legend <- tmap_moranlegendfun(londonpoints2020)

local_moran <- tmap_arrange(tm_local_moran18v, 
                            tm_local_moran19v, 
                            tm_local_moran20v, ncol=1)
local_moran
```


### Function to run Gi*

```{r}
Gi_ward_local_densityfun <- function(londonpointsyear){
  ward_lw <- ward_lwfun(londonpointsyear)
  
  Gi_ward_local_density <- londonpointsyear %>% 
    pointsjoinedfun(.) %>% 
    pull(density) %>%
    as.vector()%>%
    localG(., ward_lw)
  
  density_Gi <- londonpointsyear %>% 
    pointsjoinedfun(.) %>% 
    mutate(density_G = as.numeric(Gi_ward_local_density))
  
  return(density_Gi)
}
```


### Function to run tmap for Gi*

```{r}
tmap_Gifun <- function(londonpointsyear, number, mode){
  breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
  GIColours<- rev(brewer.pal(8, "RdBu"))
  density_Gi <- Gi_ward_local_densityfun(londonpointsyear)
  tmap_mode(mode)
  tmap <- tm_shape(density_Gi) +
    tm_polygons("density_G",
                breaks=breaks1,
                palette=GIColours,
                title="Gi*, Charge Points in London") +
    tm_legend(show=FALSE)+
    tm_layout(frame=FALSE)+
    tm_credits(number, position=c(0,0.85), size=1)
  
  return(tmap)
}
```

```{r}
G1 <- tmap_Gifun(londonpoints2018, "a)", "plot")
G2 <- tmap_Gifun(londonpoints2019, "b)", "plot")
G3 <- tmap_Gifun(londonpoints2020, "c)", "plot")
```

```{r}
tmap_Gilegendfun <- function(londonpointsyear){
  breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
  GIColours<- rev(brewer.pal(8, "RdBu"))
  density_Gi <- Gi_ward_local_densityfun(londonpointsyear)
  legend <- tm_shape(density_Gi) +
    tm_polygons("density_G",
                breaks=breaks1,
                palette=GIColours,
                title="Gi*, Charge Points in London") +
    tm_scale_bar(position=c(0.1,0.04), text.size=0.6)+
    tm_compass(north=0, position=c(0.65,0.2))+
   
    tm_layout(title = "Charge Points Gi* Density", 
              legend.title.size=1,
              legend.text.size = 0.6,
              legend.only = TRUE, 
              legend.position=c(0.1,0.25),asp=0.1)
  
  return(legend)
}
```
```{r}
Gi_legend <- tmap_Gilegendfun(londonpoints2020)

Gi <- tmap_arrange(G1, G2, G3, Gi_legend, ncol=2)
Gi
```
```{r}
tmap_save(local_moran, "pic/Gi, Charge Points in London.png",width=7, height=4)
```