
# Statistical Correlation Analysis

There are several characteristics are considered to contribute to the density of charge points (CD) and its utilization rates (UR), including socio-demographic, travel-related and land-use characteristics. In specific, they are employment rate (ER), house price (HP), public transit score (PS), which could reflect the level of local public transport), parking density (PD), percentage of residential area (RSP) and percentage of road area (RP). 

## Load packages


### Load plot library

```{r}
library(Rmisc) 
library(plyr)
```

### Load model library

```{r}
library(stats)
library(corrr)
library(car)
library(spatstat)
library(tidymodels)
library(spatialreg)
```

## Load files

### Load London wards shapefile

```{r}
londonwards <- st_read("datasets/wards/London_Ward_CityMerged.shp") %>% 
  st_transform(., 27700)
```


### Load points in wards

```{r}
points_wards <- read_csv("created datasets/points_wards.csv")
summary(points_wards)
```



### Load wards profile

Load London wards profile as the basic data frame for correlation analysis

```{r}
ward_profile <- read_csv("datasets/ward_profiles.csv",
                         col_types = cols(
                           "New code" = col_character(),
                           "% All Working-age (16-64) - 2015"= col_number(),
                           "Population density (persons per sq km) - 2013"= col_number(),
                           "Number Killed or Seriously Injured on the roads - 2014" = col_number(),
                           "Employment rate (16-64) - 2011" = col_number(),
                           "Median House Price (£) - 2014" = col_number(),
                           "Cars per household - 2011" = col_number(),
                           "Average Public Transport Accessibility score - 2014"= col_number()
                         ))
colnames(ward_profile)
head(ward_profile)
```

```{r}
londonward_code <- londonwards %>% 
  st_drop_geometry() %>% 
  clean_names() 
```
```{r}
londonward_code <- londonward_code %>% 
  dplyr::select(., c(2))
```

```{r}
wardprofile <- ward_profile %>% 
  dplyr::select(., c(1, 2, 3, 9, 14, 25, 27, 31, 64, 65)) %>% 
  clean_names() %>% 
  group_by(ward_name) %>%         
    summarise(old_code=old_code,
              gss_code=new_code,
              pop_density=population_density_persons_per_sq_km_2013,
              road_incidents=number_killed_or_seriously_injured_on_the_roads_2014,
              employment_rate=employment_rate_16_64_2011,
              houseprice=median_house_price_2014,
              car_ownership=cars_per_household_2011,
              publictransaccess_score=average_public_transport_accessibility_score_2014)%>% 
  merge(londonward_code, .,
        by.x = "gss_code",
        by.y = "gss_code") %>% 
  distinct(.,.keep_all=TRUE)


colnames(wardprofile)
```
```{r}
write.table(wardprofile,"created datasets/wardprofile.csv",row.names=FALSE,col.names=TRUE,sep=",")
```
```{r}
allcharacter <- points_wards %>% 
  left_join(wardprofile,.,
            by = c("gss_code" = "gss_code"))
```


### Load household.csv

```{r}
household <- read_csv("datasets/households-type-2001-ward.csv") %>% 
  dplyr::select(., c(1, 3)) %>% 
  clean_names()
summary(household)
```

Join household dataset to the ward profile data frame

```{r}
allcharacter <- allcharacter %>% 
  left_join(., household,
            by = c("old_code" = "area_code"))
```



### Load land use.csv

```{r}
landuse <- read_csv("datasets/land-use-glud-ward.csv") %>% 
  dplyr::select(., c(1, 3, 16, 17, 19, 20, 21)) %>% 
  clean_names() %>% 
  group_by(area_name) %>%         
    summarise(area_code=area_code,
              residential_percentage=percent_area_of_domestic_buildings+percent_area_of_domestic_gardens, road_percentage= percent_area_of_road,
              rail_percentage = percent_area_of_rail,
              path_percentage = percent_area_of_path)
              
              
summary(landuse)
```

Join landuse dataset to the ward profile data frame

```{r}
allcharacter <- allcharacter %>% 
  left_join(., landuse,
            by = c("old_code" = "area_code"))
```

### Load parking.shp

```{r}
parking <- st_read("datasets/parking/gis_osm_traffic_a_free_1.shp") %>% 
  st_transform(., 27700) 
```

Join parking dataset to the ward profile data frame

```{r}
parking <- parking[parking$fclass=="parking"|parking$fclass=="parking_multistorey"|parking$fclass=="parking_underground"|parking$fclass=="parking_site",] 

parking_london <- st_intersects(londonwards, parking)
londonparking <- parking[unlist(parking_london),]
```
```{r}
parking_ward <- londonparking[londonwards,]
parking_wards <- londonwards%>%
    st_join(parking_ward)%>%
    add_count(NAME)%>%
    janitor::clean_names() %>% 
  mutate(parking_density=(n/hectares)*1000) %>% 
  dplyr::select(gss_code, parking_density) %>% 
  distinct(., gss_code, .keep_all = TRUE)
```
```{r}
allcharacter <- allcharacter %>% 
  left_join(., parking_wards,
            by = c("gss_code" = "gss_code")) 
```

### Select independent variables

```{r}
colnames(allcharacter)
```
```{r}
allcharacter <- allcharacter %>%                    
    dplyr::select(., c(1, 9, 12, 3, 5, 6, 7, 13, 8, 18, 4, 14, 15, 16, 17))
```

```{r}
characters <- allcharacter %>% 
  mutate(userate=(car_ownership*all_households)/chargepointcount) %>% 
  dplyr::select(., c(1,2,16,4,5,6,9,10,11,12,13,14,15))
```
```{r}
colnames(characters)
```

### Save all characters.csv

```{r}
write.table(points_wards,"created datasets/characters.csv",row.names=FALSE,col.names=TRUE,sep=",")
```


## Check variable distributions

Ensure the variables could be normal distribution

### Variables

```{r}
p1 <- ggplot(data=characters, aes(x=density))+
  geom_histogram()
p2 <- ggplot(data=characters, aes(x=userate))+
  geom_histogram()
p3 <- ggplot(data=characters, aes(x=pop_density))+
  geom_histogram()
p4 <- ggplot(data=characters, aes(x=employment_rate))+
  geom_histogram()
p5 <- ggplot(data=characters, aes(x=houseprice))+
  geom_histogram()
p6 <- ggplot(data=characters, aes(x=publictransaccess_score))+
  geom_histogram()
p7 <- ggplot(data=characters, aes(x=parking_density))+
  geom_histogram()
p8 <- ggplot(data=characters, aes(x=road_incidents))+
  geom_histogram()
p9 <- ggplot(data=characters, aes(x=residential_percentage))+
  geom_histogram()
p10 <- ggplot(data=characters, aes(x=road_percentage))+
  geom_histogram()
p11 <- ggplot(data=characters, aes(x=rail_percentage))+
  geom_histogram()
p12 <- ggplot(data=characters, aes(x=path_percentage))+
  geom_histogram()
```


### Plot variable distribution

```{r}
multiplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, cols = 3)
```

### Plot log(variable) distribution

```{r}
lp1 <- ggplot(data=characters, aes(x=log(density)))+
  geom_histogram()
lp2 <- ggplot(data=characters, aes(x=log(userate)))+
  geom_histogram()
lp3 <- ggplot(data=characters, aes(x=log(pop_density)))+
  geom_histogram()
lp4 <- ggplot(data=characters, aes(x=log(employment_rate)))+
  geom_histogram()
lp5 <- ggplot(data=characters, aes(x=log(houseprice)))+
  geom_histogram()
lp6 <- ggplot(data=characters, aes(x=log(publictransaccess_score)))+
  geom_histogram()
lp7 <- ggplot(data=characters, aes(x=log(parking_density)))+
  geom_histogram()
lp8 <- ggplot(data=characters, aes(x=log(road_incidents)))+
  geom_histogram()
lp9 <- ggplot(data=characters, aes(x=log(residential_percentage)))+
  geom_histogram()
lp10 <- ggplot(data=characters, aes(x=log(road_percentage)))+
  geom_histogram()
lp11 <- ggplot(data=characters, aes(x=log(rail_percentage)))+
  geom_histogram()
lp12 <- ggplot(data=characters, aes(x=log(path_percentage)))+
  geom_histogram()
```


### Plot log(variable) distribution

```{r}
multiplot(lp1, lp2, lp3, lp4, lp5, lp6, lp7, lp8, lp9, lp10, lp11, lp12, cols = 3)
```

### Plot normal distribution


```{r}
multiplot(lp1, lp2, p3, p4, lp5, lp6, lp7, p9, p10, cols = 3)
```

### Independent variables

```{r}
independent <- characters %>% 
  dplyr::select(., c(1, 2, 3, 5, 6, 7, 8, 10, 11))
```
```{r}
colnames(independent)
```


## Correlation analysis

### Correlationship of userate & public transit of charge points in London

Remove possible outliers and plot the correlationship between these variables, comparing the charging density case and use rate case and finding the overall relationship. 

```{r}
qu1 <- qplot(x = `employment_rate`, 
             y = `userate`, 
             data=independent, 
             xlim = c(50, 85))

#plot with a regression line
qu1 <- qu1 + stat_smooth(method="lm", se=FALSE, size=1)
qd1 <- qplot(x = `employment_rate`, 
             y = `density`, 
             data=independent, 
             xlim = c(50, 85))

#plot with a regression line
qd1 <- qd1 + stat_smooth(method="lm", se=FALSE, size=1)
multiplot(qd1, qu1, cols = 2)
```
```{r}
qu2 <- qplot(x = `houseprice`, 
             y = `userate`, 
             data=independent, 
             xlim = c(250000, 800000))

#plot with a regression line
qu2 <- qu2 + stat_smooth(method="lm", se=FALSE, size=1) 
qd2 <- qplot(x = `houseprice`, 
             y = `density`,
             data=independent,
             xlim = c(250000, 800000))

#plot with a regression line
qd2 <- qd2 + stat_smooth(method="lm", se=FALSE, size=1) 
multiplot(qd2, qu2, cols = 2)
```
```{r}
qu3 <- qplot(x = `publictransaccess_score`, 
             y = `userate`, 
             data=independent)

#plot with a regression line
qu3 <- qu3 + stat_smooth(method="lm", se=FALSE, size=1) 
qd3 <- qplot(x = `publictransaccess_score`, 
             y = `density`, 
             data=independent)

#plot with a regression line
qd3 <- qd3 + stat_smooth(method="lm", se=FALSE, size=1)
multiplot(qd3, qu3, cols = 2)
```
```{r}
qu4 <- qplot(x = `parking_density`, 
             y = `userate`, 
             data=independent,
             xlim = c(0, 500))

#plot with a regression line
qu4 <- qu4 + stat_smooth(method="lm", se=FALSE, size=1)
qd4 <- qplot(x = `parking_density`, 
             y = `density`, 
             data=independent,
             xlim = c(0, 500))

#plot with a regression line
qd4 <- qd4 + stat_smooth(method="lm", se=FALSE, size=1)
multiplot(qd4, qu4, cols = 2)
```
```{r}
qu5 <- qplot(x = `residential_percentage`, 
             y = `userate`, 
             data=independent)

#plot with a regression line
qu5 <- qu5 + stat_smooth(method="lm", se=FALSE, size=1)
qd5 <- qplot(x = `residential_percentage`, 
             y = `density`, 
             data=independent)

#plot with a regression line
qd5 <- qd5 + stat_smooth(method="lm", se=FALSE, size=1)
multiplot(qd5, qu5, cols = 2)
```
```{r}
qu6 <- qplot(x = `road_percentage`, 
             y = `userate`, 
             data=independent)

#plot with a regression line
qu6 <- qu6 + stat_smooth(method="lm", se=FALSE, size=1)
qd6 <- qplot(x = `road_percentage`, 
             y = `density`, 
             data=independent)

#plot with a regression line
qd6 <- qd6 + stat_smooth(method="lm", se=FALSE, size=1)
multiplot(qd6, qu6, cols = 2)
```




