

# Regression Analysis

In order to forecast charging facility location selection for future, the following part will compare the charge points registration distribution with other characteristics mentioned above, including land-use, travel-related and socio-demographic characteristics, applying ordinary least squares (OLS) regression models. In order to achieve higher accuracy for the results, Spatial Lag Model (SLM) which involves a separate spatially lagged variant of the dependent variable as an independent variable of the model, as well as Spatial Error Model (SEM) which incorporates a spatial lag of the OLS regression model’s residual as an independent variable, all participate in the comparison.

## Ordinary Least Squares (OLS) regression model

Find the specific relationship between those different variables

```{r}
# regression model
model1 <- lm(log(userate) ~
               employment_rate+
               log(houseprice)+
               log(publictransaccess_score)+
               log(parking_density)+
               residential_percentage+
               road_percentage, 
             data = independent)
```
```{r}
#show the summary of those outputs
summary(model1)
glance(model1)
```
```{r}
m1_tidy <- model1 %>% 
  tidy() 
m1_tidy
```
```{r}
# regression model
model2 <- lm(log(density) ~ 
               employment_rate+
               log(houseprice)+
               log(publictransaccess_score)+
               log(parking_density)+
               residential_percentage+
               road_percentage, 
             data = characters)
```
```{r}
#show the summary of those outputs
summary(model2)
glance(model2)
```

## Assumptions Underpinning Linear Regression

### Assumption 1 - There is a linear relationship between the dependent and independent variables

```{r}
multiplot(lp1, lp2, p4, lp5, lp6, lp7, p9, p10, cols = 3)
```

### Assumption 2 - The residuals in your model should be normally distributed

```{r}
#save the residuals into dataframe

model1_data <- model1 %>%
  augment(., independent)

#plot residuals
model1_data%>%
dplyr::select(.resid)%>%
  pull()%>%
  qplot()+ 
  geom_histogram() 
```
```{r}
#save the residuals into dataframe

model2_data <- model2 %>%
  augment(., independent)

#plot residuals
model2_data%>%
dplyr::select(.resid)%>%
  pull()%>%
  qplot()+ 
  geom_histogram() 
```


### Assumption 3 - No Multicolinearity in the independent variables

```{r}
position <- c(2:9)

Correlation_all<- independent %>%
  dplyr::select(position)%>%
    correlate()
Correlation_all
```
```{r}
position <- c(4:9)

Correlation<- independent %>%
  dplyr::select(position)%>%
  dplyr::rename(ER="employment_rate",
         HP="houseprice",
         PS="publictransaccess_score",
         PD="parking_density",
         RSP="residential_percentage",
         RP="road_percentage"
         ) %>% 
    correlate()
r <- rplot(Correlation, shape = 15,colours = c("skyblue1", "white", "indianred2"))
r
```
```{r}
png(filename = "pic/correlation.png", 
    width = 500, height = 500)     
r
dev.off()
```


### Assumption 4 - Homoscedasticity

```{r}
par(mfrow=c(2,2)) 
plot(model1)
```
```{r}
par(mfrow=c(2,2)) 
plot(model2)
```

### Assumption 5 - Independence of Errors

```{r}
#run durbin-watson test m1
DW1 <- durbinWatsonTest(model1)
tidy(DW1)
```

```{r}
#run durbin-watson test m2
DW2 <- durbinWatsonTest(model2)
tidy(DW2)
```

```{r}
residuals <- londonwards %>% 
  mutate(model1residual = residuals(model1)) %>% 
  mutate(model2residual = residuals(model2))
```

```{r}
#plot the residuals m1
tmap_mode("view")
qtm(residuals, fill = "model1residual")

```
```{r}
#plot the residuals m2
tmap_mode("view")
qtm(residuals, fill = "model2residual")
```

### Moran's I test for residuals (generally)

```{r}
coordsW <- residuals %>% 
    st_centroid() %>%
    st_geometry()
```
```{r}
# queen
queen_nb <- residuals %>%
  poly2nb(., queen=T)

# k nearest neighbours
knn_nb <-coordsW %>%
  knearneigh(., k=9)%>%
  knn2nb()
```

```{r}
#create spatial weights matrix 

queens_weight <- queen_nb %>%
  nb2listw(., style="C")

knn_weight <- knn_nb %>%
  nb2listw(., style="C")
```

```{r}
Queen1 <- residuals %>%
  st_drop_geometry()%>%
  dplyr::select(model1residual)%>%
  pull()%>%
  moran.test(., queens_weight)%>%
  tidy()
Queen1
```

```{r}
Knn1 <- residuals %>%
  st_drop_geometry()%>%
  dplyr::select(model1residual)%>%
  pull()%>%
  moran.test(., knn_weight)%>%
  tidy()
Knn1
```

```{r}
Queen2 <- residuals %>%
  st_drop_geometry()%>%
  dplyr::select(model2residual)%>%
  pull()%>%
  moran.test(., queens_weight)%>%
  tidy()
Queen2
```

```{r}
Knn2 <- residuals %>%
  st_drop_geometry()%>%
  dplyr::select(model2residual)%>%
  pull()%>%
  moran.test(., knn_weight)%>%
  tidy()
Knn2
```

## Spatial Regression Models

### Spatial Lag models for Model 1 (queen)


```{r}
lag_model1_queen <- lagsarlm(log(userate) ~
                               employment_rate+
                               log(houseprice)+
                               log(publictransaccess_score)+
                               log(parking_density)+
                               residential_percentage+
                               road_percentage,
                             data = independent, 
                             nb2listw(queen_nb, style="C"), 
                             method = "eigen")

tidy(lag_model1_queen)
glance(lag_model1_queen)
```

### Spatial Lag models for Model 2 (queen)

```{r}
lag_model2_queen <- lagsarlm(log(density) ~
                               employment_rate+
                               log(houseprice)+
                               log(publictransaccess_score)+
                               log(parking_density)+
                               residential_percentage+
                               road_percentage,
                             data = independent, 
                             nb2listw(queen_nb, style="C"), 
                             method = "eigen")

tidy(lag_model2_queen)
glance(lag_model2_queen)
```

### Spatial Error models for Model 1 (queen)

```{r}
error_model1_queen <- errorsarlm(log(userate) ~
                                   employment_rate+
                                   log(houseprice)+
                                   log(publictransaccess_score)+
                                   log(parking_density)+
                                   residential_percentage+
                                   road_percentage,
                                 data = independent, 
                                 nb2listw(queen_nb, style="C"), 
                                 method = "eigen")

tidy(error_model1_queen)
glance(error_model1_queen)
```

### Spatial Error models for Model 2 (queen)

```{r}
error_model2_queen <- errorsarlm(log(density) ~
                                   employment_rate+
                                   log(houseprice)+
                                   log(publictransaccess_score)+
                                   log(parking_density)+
                                   residential_percentage+
                                   road_percentage,
                                 data = independent, 
                                 nb2listw(queen_nb, style="C"), 
                                 method = "eigen")

tidy(error_model2_queen)
glance(error_model2_queen)
```



### Find best k for KNN strategy

Use for loop to find the best k (1 to 10) for those Spatial Regression Models, and summarize the best k values, corresponding R-squared and AIC, so that they can be compared and the better results can be identified for further analysis.

#### The k for Spatial Lag Model 1


```{r}
r_squared <- list()
best_k <- list()
AIC <- list()
# create empty variable to store fit
k <- NA
a <- NA
  
# run the k-means 10 times
for (i in 1:10){
  
  # keep track of the runs
  print(paste0('starting run: k = ', i))
  coordsW <- residuals %>% 
    st_centroid() %>%
    st_geometry()
  knn_nb <-coordsW %>%
  knearneigh(., k=i)%>%
  knn2nb()
  
  knn_weight <- knn_nb %>%
  nb2listw(., style="C")
  
  lag_model1_knni <- lagsarlm(log(userate) ~
                              employment_rate+
                              log(houseprice)+
                              log(publictransaccess_score)+
                              log(parking_density)+
                              residential_percentage+
                              road_percentage,
                            data = independent, 
                            nb2listw(knn_nb, style="C"), 
                            method = "eigen")

  k[i] <- glance(lag_model1_knni)[[1]]
  a[i] <- glance(lag_model1_knni)[[2]]
  
  # update the results of the clustering if the total within sum of squares for the run
  # is lower than any of the runs that have been executed so far 
  if (k[i] > max (k[1:(i-1)])){
    r_squared <- k[i]
    best_k <- i
    AIC <- a[i]}
}

```
```{r}
r_squared 
best_k 
AIC
```

#### The k for Spatial Lag Model 2

```{r}
r_squared2 <- list()
best_k2 <- list()
AIC2 <- list()
# create empty variable to store fit
k <- NA
a <- NA
  
# run the k-means 10 times
for (i in 1:10){
  
  # keep track of the runs
  print(paste0('starting run: k = ', i))
  coordsW <- residuals %>% 
    st_centroid() %>%
    st_geometry()
  knn_nb <-coordsW %>%
  knearneigh(., k=i)%>%
  knn2nb()
  
  knn_weight <- knn_nb %>%
  nb2listw(., style="C")
  
  lag_model2_knni <- lagsarlm(log(density) ~
                              employment_rate+
                              log(houseprice)+
                              log(publictransaccess_score)+
                              log(parking_density)+
                              residential_percentage+
                              road_percentage,
                            data = independent, 
                            nb2listw(knn_nb, style="C"), 
                            method = "eigen")

  k[i] <- glance(lag_model2_knni)[[1]]
  a[i] <- glance(lag_model2_knni)[[2]]
  
  # update the results of the clustering if the total within sum of squares for the run
  # is lower than any of the runs that have been executed so far 
  if (k[i] > max (k[1:(i-1)])){
    r_squared2 <- k[i]
    best_k2 <- i
    AIC2 <- a[i]}
}

```
```{r}
r_squared2
best_k2 
AIC2
```


#### The k for Spatial Error Model 1


```{r}
r_squared3 <- list()
best_k3 <- list()
AIC3 <- list()
# create empty variable to store fit
k <- NA
a <- NA
  
# run the k-means 10 times
for (i in 1:10){
  
  # keep track of the runs
  print(paste0('starting run: k = ', i))
  coordsW <- residuals %>% 
    st_centroid() %>%
    st_geometry()
  knn_nb <-coordsW %>%
  knearneigh(., k=i)%>%
  knn2nb()
  
  knn_weight <- knn_nb %>%
  nb2listw(., style="C")
  
  error_model1_knni <- errorsarlm(log(userate) ~
                                  employment_rate+
                                  log(houseprice)+
                                  log(publictransaccess_score)+
                                  log(parking_density)+
                                  residential_percentage+
                                  road_percentage,
                                data = independent, 
                                nb2listw(knn_nb, style="C"), 
                                method = "eigen")

  k[i] <- glance(error_model1_knni)[[1]]
  a[i] <- glance(error_model1_knni)[[2]]
  
  # update the results of the clustering if the total within sum of squares for the run
  # is lower than any of the runs that have been executed so far 
  if (k[i] > max (k[1:(i-1)])){
    r_squared3 <- k[i]
    best_k3 <- i
    AIC3 <- a[i]}
}

```
```{r}
r_squared3
best_k3 
AIC3
```

#### The k for Spatial Error Model 2

```{r}
r_squared4 <- list()
best_k4 <- list()
AIC4 <- list()
# create empty variable to store fit
k <- NA
a <- NA
  
# run the k-means 10 times
for (i in 1:10){
  
  # keep track of the runs
  print(paste0('starting run: k = ', i))
  coordsW <- residuals %>% 
    st_centroid() %>%
    st_geometry()
  knn_nb <-coordsW %>%
  knearneigh(., k=i)%>%
  knn2nb()
  
  knn_weight <- knn_nb %>%
  nb2listw(., style="C")
  
  error_model2_knni <- errorsarlm(log(density) ~
                                  employment_rate+
                                  log(houseprice)+
                                  log(publictransaccess_score)+
                                  log(parking_density)+
                                  residential_percentage+
                                  road_percentage,
                                data = independent, 
                                nb2listw(knn_nb, style="C"), 
                                method = "eigen")

  k[i] <- glance(error_model2_knni)[[1]]
  a[i] <- glance(error_model2_knni)[[2]]
  
  # update the results of the clustering if the total within sum of squares for the run
  # is lower than any of the runs that have been executed so far 
  if (k[i] > max (k[1:(i-1)])){
    r_squared4 <- k[i]
    best_k4 <- i
    AIC4 <- a[i]}
}

```
```{r}
r_squared4 
best_k4 
AIC4
```


### Spatial Error models for Model 1 (KNN; k=9)


```{r}
error_model1_knn9 <- errorsarlm(log(userate) ~
                                  employment_rate+
                                  log(houseprice)+
                                  log(publictransaccess_score)+
                                  log(parking_density)+
                                  residential_percentage+
                                  road_percentage,
                                data = independent, 
                                nb2listw(knn_nb, style="C"), 
                                method = "eigen")

tidy(error_model1_knn9)
glance(error_model1_knn9)
```
```{r}
error_model2_knn9 <- errorsarlm(log(density) ~
                                  employment_rate+
                                  log(houseprice)+
                                  log(publictransaccess_score)+
                                  log(parking_density)+
                                  residential_percentage+
                                  road_percentage,
                                data = independent, 
                                nb2listw(knn_nb, style="C"), 
                                method = "eigen")

tidy(error_model2_knn9)
glance(error_model2_knn9)
```

#### Check residuals

Check wether the residuals of the better model still show spatial correlation. 

```{r}
# residuals for spatial error model 1

residuals <- residuals %>%
  mutate(error_model1_knn9_resids = residuals(error_model1_knn9))

ErrorMoran1 <- residuals %>%
  st_drop_geometry()%>%
  dplyr::select(error_model1_knn9_resids)%>%
  pull()%>%
  moran.test(., knn_weight)%>%
  tidy()

ErrorMoran1
```

```{r}
# residuals for spatial error model 2

residuals <- residuals %>%
  mutate(error_model2_knn9_resids = residuals(error_model2_knn9))

ErrorMoran2 <- residuals %>%
  st_drop_geometry()%>%
  dplyr::select(error_model2_knn9_resids)%>%
  pull()%>%
  moran.test(., knn_weight)%>%
  tidy()

ErrorMoran2
```

